Verifying Demonstrations

### 2019-07-16 paper/related-work.tex
Adds related work

\section{Related work}%
\label{related-work}

\subsection{Crowd counting methods}
\input{crowd-counting-methods.tex}

\subsection{Location proofs}
\input{location-proofs.tex}

>>>>

\section{Related work}

Our scheme relates to several other works: the crowd counting methods already 
described in \cref{current-crowd-counting}, location-proof systems and 
Sybil-free pseudonym systems.

\paragraph*{Location-proof systems}%
\label{db-and-lp}

Some \acp{LBS} only grant access to resources to users located at a particular 
location, thus raising the issue of verifying the position claimed by a 
particular user.
In most of the existing schemes, the location of a user (device) is determined 
by the device itself (\eg through GPS) and forwarded to the \ac{LBS} provider.
One of the main drawbacks of this approach is that a user can cheat by having 
her device transmit a false location.

One possible way to counter this threat is to request the device to prove that 
it really is at the claimed location, which gives rise to the concept of 
\acp{LP}.
In a nutshell, \iac{LP} is a digital certificate attesting that someone was at 
a particular location at a specific moment in time.
\Iac{LPS} is an architecture by which users can obtain \acp{LP} from 
neighboring witnesses (\eg trusted access points or other users) that can later 
be shown to verifiers who can check the validity of a particular 
proof~\cite{luo2010veriplace,zhu2011applaus}.
Most of the existing approaches to \acp{LP} require the prover and the 
witnesses to disclose their identities, thus raising many privacy issues such 
as the possibility of tracing the movements of users of the \ac{LPS}.
However, some \acp{LPS}, such as PROPS~\cite{PROPS}, exist that provide strong 
privacy guarantees along with the possibility of verifying the claim of the 
location.

\CROCUS shares some similarities with PROPS\@.
The main difference is that \CROCUS operates in a more adverse environment, and 
can thus not provide any guarantees using the decentralized, untrusted 
witnesses that PROPS can.
The incentives to cheat are also bigger and consequently the thresholds for 
collusion are much higher.
(The same can be said in comparison to Platin.io\footnote{%
  URL: \url{https://platin.io}.
}.)
CROCUS must also tie the cause to the location proof, to designate the proof 
to the protest in which the protester participated.

\paragraph*{Sybil-free pseudonym systems}

Our Sybil-free pseudonym system is very similar to that of 
\textcite{SybilFreePseudonyms}.
Both are based on the work of \textcite{HowToWinTheCloneWars}.
We make the same simplification of~\cite{HowToWinTheCloneWars} as 
\textcite{SybilFreePseudonyms}, but we also require an interactive version.
Furthermore, our \acp{PK} must be distance bounding.
